Should geophysicists use the gravity disturbance or the anomaly?

### 2018-06-20 manuscript/letter.tex
insert missing boldsymbol gamma

\begin{equation}
\mathbf{g}_i = \mathbf{\gamma}_i + \delta \mathbf{g}_i \: .
\label{eq:gravity-vector-TCS}
\end{equation}

\noindent
Furthermore, the gravity $g_i$ can be approximated by a first order Taylor's
expansion \citep{sanso_sideris2013}:

\begin{equation}
g_i \approx \gamma_i +
\mathbf{\gamma}_i^{\top} \delta \mathbf{g}_i \: ,
\label{eq:gobs-approx}
\end{equation}

\noindent
where $^{\top}$ denotes transposition and $\mathbf{\gamma}_{i}$ is a unit
vector with the direction of the normal gravity vector.
This approximation is valid because
$\gamma_{i} \gg \| \delta \mathbf{g}_{i} \|$ at all points on or above the
Earth's surface.
It is known in geodesy \citep[e.g.,][]{sanso_sideris2013}
and is analogous to the approximation used for
total-field magnetic anomalies \citep[e.g.,][]{blakely1996}.
In local or regional scales, the unit
vector $\mathbf{\gamma}_{i}$
may be considered constant throughout the study area and
parallel to the $z$ axis of the TCS (Figure \ref{fig:systems}c).

Using equation \ref{eq:gobs-approx} and fixing $\gamma$ at a point $P$ at
the origin of the TCS (Figure \ref{fig:systems}c),
the gravity disturbance can be rewritten as:

\begin{equation}
\delta g_{i} \approx \mathbf{\gamma}_{P}^{\top} \delta \mathbf{g}_{i} \: .
\label{eq:gravity-disturbance-approx-TCS}
\end{equation}

\noindent
This equation shows that the gravity disturbance $\delta g_{i}$ is
approximately the component of the $\delta \mathbf{g}_{i}$ in the direction of
the normal gravity vector $\mathbf{\gamma}_P$
\citep{hofmann-wellenhof-moritz2005, sanso_sideris2013}.
Because $z$-axis of the TCS is parallel to $\mathbf{\gamma}_P$
(Figure \ref{fig:surfaces}), the gravity disturbance can be defined as the
$z$-component of the gravitational attraction exerted by the gravity sources at
the point $(x_{i}, y_{i}, z_{i})$.
As a consequence, the gravity disturbance can be modelled by the harmonic
function:

>>>>

\begin{equation}
\mathbf{g}_i = \boldsymbol{\gamma}_i + \delta \mathbf{g}_i \: .
\label{eq:gravity-vector-TCS}
\end{equation}

\noindent
Furthermore, the gravity $g_i = \| \mathbf{g}_i \|$ can be approximated by a first order Taylor's
expansion \citep{sanso_sideris2013}:

\begin{equation}
g_i \approx \gamma_i +
\hat{\boldsymbol{\gamma}}_i^{\top} \delta \mathbf{g}_i \: ,
\label{eq:gobs-approx}
\end{equation}

\noindent
where $^{\top}$ denotes transposition, $\gamma_i = \| \boldsymbol{\gamma}_i \|$ 
and $\hat{\boldsymbol{\gamma}}_{i}$ is a unit
vector with the direction of the normal gravity vector.
This approximation is valid because
$\gamma_{i} \gg \| \delta \mathbf{g}_{i} \|$ at all points on or above the
Earth's surface.
It is known in geodesy \citep[e.g.,][]{sanso_sideris2013}
and is analogous to the approximation used for
total-field magnetic anomalies \citep[e.g.,][]{blakely1996}.
In local or regional scales, the unit
vector $\hat{\boldsymbol{\gamma}}_{i}$
may be considered constant throughout the study area and
parallel to the $z$ axis of the TCS (Figure \ref{fig:systems}c).

Using equation \ref{eq:gobs-approx} and fixing 
$\hat{\boldsymbol{\gamma}}_{i}$ at a point $P$ at
the origin of the TCS (Figure \ref{fig:systems}c),
the gravity disturbance can be rewritten as:

\begin{equation}
\delta g_{i} \approx \hat{\boldsymbol{\gamma}}_{P}^{\top} \delta \mathbf{g}_{i} \: .
\label{eq:gravity-disturbance-approx-TCS}
\end{equation}

\noindent
This equation shows that the gravity disturbance $\delta g_{i}$ is
approximately the component of the $\delta \mathbf{g}_{i}$ in the direction of
the normal gravity vector $\boldsymbol{\gamma}_P$
\citep{hofmann-wellenhof-moritz2005, sanso_sideris2013}.
Because $z$-axis of the TCS is parallel to $\boldsymbol{\gamma}_P$
(Figure \ref{fig:surfaces}), the gravity disturbance can be defined as the
$z$-component of the gravitational attraction exerted by the gravity sources at
the point $(x_{i}, y_{i}, z_{i})$.
As a consequence, the gravity disturbance can be modelled by the harmonic
function:
